\documentclass[margin-section]{resume}

% default to the abridged version
\providecommand{\ifunabridged}{\iffalse}

\begin{document}

% Heading information
\name{Adrian Trunzo}
\address{10 Cedar Trail\\East Hampton, NY 11937}
\address{(631) 413-2205\\adriantrunzo@outlook.com\\github.com/adriantrunzo}

\begin{resume}

    % Summary -----------------------------------------------------------------
    \section{Summary}

    I need to write a summary.

    % Technical Skills --------------------------------------------------------
    \section{Skills}

    \textbf{Expert:} Python, HTML/CSS, JavaScript, SQL, Git/Mercurial, OS X,
    Linux/Unix, Vim\\
    \textbf{Experienced:} C, Objective-C, PHP, Java, Bash, Jenkins CI


    % Education ---------------------------------------------------------------
    \section{Education}

    \employer{Carleton College}
    \title{Bachelor of Arts in Computer Science}
    \dates{September 2008 -- March 2012}
    \location{Northfield, MN}

    \begin{position}
        Graduated Magna Cum Laude and with distinction in major.

        Relevant Coursework: Algorithms, Natural Language Processing,
        Database Systems, Computer Networks, Software Design, Programming
        Languages, Artificial Intelligence, Computer Organization and
        Architecture, Statistics
    \end{position}


    % Professional Experience -------------------------------------------------
    \section{Work\\Experience}

    % Ultralingua jobs
    \employer{Ultralingua Inc.}
    \location{Minneapolis, MN}

    \title{Software Developer}
    \dates{April 2012 -- May 2013}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Developed multiple internal web services providing backend
            functionality to the company's most popular products.
        \item Maintained several Linux servers and provided support to fellow
            employees.
        \item Contributed to the codebase of the company's core iOS products,
            implementing customer requested features and fixing bugs.
        \item Planned and initiated a redesign of the company's website.
    \end{list2}
    \end{position}

    \title{Software Developer Intern}
    \dates{June 2011 -- August 2011}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
    \item Developed and deployed an internal web application for editing
        large, multilingual dictionary datasets.
    \end{list2}
    \end{position}

    % Carleton student jobs
    \employer{Carleton College}
    \location{Northfield, MN}

    \title{Computer Science Lab Assistant}
    \dates{September 2010 -- March 2012}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Assisted students with introductory and intermediate classwork.
        \item Provided support for Mac OS X, BASH, {\LaTeX} and several
            programming languages.
    \end{list2}
    \end{position}

    \title{Computer Science Grader}
    \dates{September 2010 -- November 2011}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Graded assignments for CS 208: Computer Organization and
            Architecture, CS 204: Software Design and CS 251: Programming
            Languages.
        \item Evaluated assignments for correctness and provided extensive
            feedback on programming style and practices.
    \end{list2}
    \end{position}

    \ifunabridged
    \title{German Teaching Assistant}
    \dates{January 2010 -- June 2010}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Taught two one hour sessions of intermediate German per week.
        \item Assisted professors and other TAs in creating new lesson plans and
        activities.
    \end{list2}
    \end{position}
    \fi

    % Summer jobs
    \ifunabridged
    \employer{Geekhampton}
    \location{Sag Harbor, NY}

    \title{Apple Technician}
    \dates{Summer/Winter 2009-10, Current}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Diagnosed and repaired Apple products, performed data recovery,
        provided technical support and knowledge to customers.
    \item Completed Apple Certified Mac Technician (ACMT) training.
    \end{list2}
    \end{position}
    \fi


    % Projects ----------------------------------------------------------------
    \section{Projects}

    \begin{format}
    \title{l}\dates{r}\\
    \body\\
    \end{format}

    \title{Trunzo Building Contractors, Inc.}
    \dates{April 2013 -- Current}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Designed and developed trunzobuilding.com for Trunzo
            Building Contractors, Inc. using Drupal with a custom
            theme and modules.
        \item Actively maintain the codebase and provide support for the
            content authors.
    \end{list2}
    \end{position}

    \title{Internet Personal Assistant}
    \dates{September 2011 -- March 2012}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Worked in a five person team to develop a web application allowing
            users to define actions triggered by various internet sources.
        \item Implemented a Flask/PostgreSQL backend and an accessible, jQuery
            powered frontend.
    \end{list2}
    \end{position}


    % Certifications ----------------------------------------------------------
    \ifunabridged
    \section{Certifications}

    \title{Apple Certified Mac Technician}
    \dates{August 2009 -- Current}

    \begin{position}
    \vspace{-\baselineskip}
    \end{position}
    \fi

    % References --------------------------------------------------------------
    %\section{References}

    %\textbf{}

\end{resume}
\end{document}
